---
title: "Peters_Lab7_results"
author: "Nick Peters"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r necessary-libraries}
library(tidyverse)
```

### 1. Read IMDBMoviesexercise.csv, IMDBMoviesRevenueExercise.csv into Rstudio and merge two datasets by Title.

#### Hint: you may need to clean the data (See R exercise 22).

```{r import-merge-clean}
movie_data = read.csv(file="IMDBMoviesExercise.csv")
revenue_data = read.csv(file="IMDBMoviesRevenueExercise.csv")
movie_revenue_data = merge(movie_data, revenue_data, by="Title")

anyNA(movie_revenue_data$Revenue)
anyNA(movie_revenue_data$Runtime)
anyNA(movie_revenue_data$Rating)

movie_revenue_data = drop_na(movie_revenue_data, "Revenue")
```

### 2. What is the correlation coefficient between Revenue and Run-time?

```{r revenue-runtime-correlation-matrix}       
cor(movie_revenue_data$Revenue, movie_revenue_data$Runtime)
```

### 3. Plot the linear regression line on the scatterplot of Revenue (Y) vs. Rating (X).

```{r plot-rating-vs-revenue}       
revenue_v_rating = lm(Revenue~Rating, movie_revenue_data)
plot(Revenue~Rating, data=movie_revenue_data,
      xlab="Rating",
      ylab="Revenue in Millions of Dollars ($)",
     main="Rating vs. Revenue")
abline(revenue_v_rating, col="red")
```

### 4. Plot the linear regression line on the scatterplot of Rating (Y) vs. Runtime (X).

```{r plot-runtime-vs-rating}   
revenue_v_rating = lm(Rating~Runtime, movie_revenue_data)
plot(Rating~Runtime, data=movie_revenue_data,
      xlab="Runtime (Minutes)",
      ylab="Rating",
      main="Runtime vs. Rating")
abline(revenue_v_rating, col="red")
```

### 5. Explain the relationships you have obtained in (3) & (4).
##### As seen by the first graph, there is a low positive correlation between Rating and Revenue, nearing close to no correlation. 
##### As seen by the second graph, there is a low positive correlation bewteen Runtime and Rating, having a slightly better correlation than Rating and Revenue.
