---
title: "Peters_HW7_results"
author: "Nick Peters"
date: "2024-11-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r import-packages}
library(tidyverse)
```

### 1. Read vg data.csv into Rstudio.
``` {r read-csv}
vg_data = read.csv(file="vg_data.csv")
```

### 2. How many rows in the data file?
``` {r num-rows}
nrow(vg_data)
```

### 3. Use glimpse to preview the data.
``` {r glimpse-data}
glimpse(vg_data)
```

### 4. How many of the video games are in the ”Puzzle” Genre?
``` {r puzzle-games}
vg_data %>%
    filter(Genre=="Puzzle") %>% 
    nrow()
```

### 5. What are the titles of the top 3 video games in the “NA Sales” variables? List only the Name.
``` {r top-NA-games}
vg_data %>%
    arrange(desc(NA_Sales)) %>%
    top_n(3) %>%
    select("Name")
```

### 6. Group the data by Genre. What is the mean JP Sales for each Genre?
``` {r mean-jp-sales-by-genre}
vg_data %>%
    group_by(Genre) %>%
    summarize(
      mean(JP_Sales)
    )
```

### 7. What is the average Global Sales for the NES Platform with in the ”Platform” Genre?
``` {r mean-global-sales-NES-platformer}
vg_data %>%
    filter(Platform=="NES", Genre=="Platform") %>%
    summarize(
      mean(Global_Sales)
    )
```

### 8. What is the correlation coefficient between JP Sales and NA Sales for the entire dataset? What is the correlation coefficient between Global Sales and NA Sales for the entire dataset?
``` {r correlation-coefficients}
cor(vg_data$JP_Sales, vg_data$NA_Sales)
cor(vg_data$Global_Sales, vg_data$NA_Sales)
```

### 9. Use lm to calculate a linear regression between Global Sales and NA Sales. Plot the scatter plot and linear regression line. Change the x-label, y-label, and title.
``` {r sales-linear-regression}
sales_model = lm(Global_Sales~NA_Sales, vg_data)
plot(Global_Sales~NA_Sales, data=vg_data,
     xlab="NA Sales",
     ylab="Global Sales",
     main="North American Sales vs. Global Sales")
abline(sales_model, col="blue")
```

### 10. There appears to be an outlier in the data (that has Global Sales over 80 and NA Sales over 40). Write R code to identify the name, Platform, Year, and Genre of this game.
``` {r find-outlier}
vg_data %>%
    filter(Global_Sales>80, NA_Sales>40) %>%
    select("Name", "Platform", "Year", "Genre")
```