---
title: "Peters_HW6_results"
author: "Nick Peters"
date: "2024-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r library-tidyverse, include=FALSE}
library(tidyverse)
```

### 1. Read telecom.csv data using the following code:
``` {r import-data}
churn_data = read.csv(file = 'telecom.csv', na.strings="")
glimpse(churn_data)
```

### 2. Clean the churn_data as follows
#### i. Drop all other columns except customerID, Monthly.Charges, Total.Charges, and Churn.
``` {r drop-unecessary-columns}
churn_data = churn_data[c("customerID","Monthly.Charges","Total.Charges","Churn")]
colnames(churn_data)
```

#### ii. Rename columns Monthly.Charges as Monthly_Charges and Total.Charges as Total_Charges.
``` {r rename-columns}
churn_data = rename(churn_data,
          Monthly_Charges=Monthly.Charges,
          Total_Charges=Total.Charges)
colnames(churn_data)
```

#### iii. Filter Data (Drop NA values in Churn column).
``` {r drop-NA}
glimpse(churn_data$Churn)
churn_data = drop_na(churn_data,"Churn")
glimpse(churn_data$Churn)
```

#### iv. Remove duplicates in the updated data set.
``` {r remove-duplicates}
churn_data = distinct(churn_data)
glimpse(churn_data)
```
#### v. Eliminate the commas, $ sign, and convert to a numeric format for both Total_Charges and Monthly_Charges columns.
``` {r transform-columns}
churn_data$Total_Charges = as.numeric(str_replace_all(churn_data$Total_Charges,"[$,]",""))
glimpse(churn_data$Total_Charges)
churn_data$Monthly_Charges = as.numeric(str_replace_all(churn_data$Monthly_Charges,"[$]",""))
glimpse(churn_data$Monthly_Charges) 
```

### 3. What percentage of the people indicated “yes” they have churned?
``` {r count-yes-churned}
churn_data$Churn == "Yes"
sum(churn_data$Churn == "Yes")/nrow(churn_data)*100
```

### 4. What is the average monthly charges for those that churned?
``` {r average-charges-churned}
yes_churn_data = subset(churn_data,churn_data$Churn=="Yes")
mean(yes_churn_data$Monthly_Charges)
```

### 5. What is the average monthly charges for those that stayed?
``` {r average-charges-stayed}
no_churn_data = subset(churn_data,churn_data$Churn=="No")
mean(no_churn_data$Monthly_Charges)
```

### 6. What is the median total charges?
``` {r median-total-charges}
median(churn_data$Total_Charges)
```
