---
title: "Peters_Lab8_results"
author: "Nick Peters"
date: "2024-11-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r import-library}
library(tidyverse)
```

### 1. Get Diamonds data set in tidyverse package and explore the data set.
``` {r explore-data}
data(diamonds)
glimpse(diamonds)
```

### 2. Plot carat vs. price by mapping color variable in the data set to the color aesthetic.
#### Hint: use ggplot with geom point.
``` {r color-aesthetic}
ggplot(diamonds, aes(carat, price, color=color)) + geom_point()
```

### 3. Define a new variable called new color as follows
#### • If the cut is Fair, then red,
#### • If the cut is Good, then blue,
#### • Otherwise, green
``` {r conditional-color}
new_color = ifelse(diamonds$cut=="Fair", "red",
                   ifelse(diamonds$cut=="Good", "blue", "green"))
glimpse(new_color)
```

### 4. Finally, plot carat vs. price by mapping new color to the color aesthetic.
``` {r new-color-aesthetic}
ggplot(diamonds, aes(carat, price, color=new_color)) + geom_point() +
  scale_color_manual(values=c("blue", "green", "red"))
```