---
title: "Peters_HW8_results"
author: "Nick Peters"
date: "2024-11-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r import-libraries}
library(tidyverse)
```

### 1. Read iris data in the datasets library.
``` {r read-iris}
head(iris)
```

### 2. How many rows in the data file?
``` {r nrow-iris}
nrow(iris)
```

### 3. Use glimpse to preview the data.
``` {r glimpse-iris}
glimpse(iris)
```

### 4. Get a basic scatter plot using ggplot for Sepal.Length vs Sepal.Width.
``` {r length-vs-width-scatter}
ggplot(iris, aes(Sepal.Length, Sepal.Width)) + geom_point()
```

### 5. Improve the plot in (4) by increasing the size of points and setting different colors for the points corresponding to each species.
``` {r inproved-scatter}
ggplot(iris, aes(Sepal.Length, Sepal.Width, color=Species)) + geom_point(size=5)
```

### 6. Add a trend line (regression line) to the data and suppress the confidence band.
``` {r scatter-with-trend}
ggplot(iris, aes(Sepal.Length, Sepal.Width)) + geom_point(size=5) +
  geom_smooth(method="lm", se=F)
```

### 7. Use different shapes for the different species and regenerate the plot in (5).
``` {r different-shapes}
ggplot(iris, aes(Sepal.Length, Sepal.Width, color=Species, shape=Species)) + geom_point(size=5)
```

### 8. Connect the points in (7) and get a line graph.
#### Hint: geom line()
``` {r line-graph}
ggplot(iris, aes(Sepal.Length, Sepal.Width, color=Species, shape=Species)) + geom_point(size=5) +
  geom_line()
```

### 9. Generate a histogram for Petal.Length variable and fill red color.
#### Hint: geom histogram() with additional commands
``` {r hisogram}
ggplot(iris, aes(Petal.Length)) + geom_histogram(bins=39, fill="red")
```

### 10. Generate a boxplot for Species vs Sepal.Width and fill lightgreen color.
``` {r boxplot}
ggplot(iris, aes(Species, Sepal.Width)) + geom_boxplot(fill="lightgreen")
```